An asymptotically normal out-of-sample test of equal predictive accuracy for nested models

### 2014-10-29 mixedwindow.tex
Extensive rewrite of supporting results
- Fix the proofs
- Add results over R+1,...,R'

\documentclass[12pt,fleqn]{article}
\input{tex/setup}
\input{tex/mcDef}
\input{tex/ap}

% These commands are generated when the Monte Carlo and applied
% sections are run; I'm giving them definitions now so that LaTeX will
% compile the document even if that code hasn't been run yet.
\providecommand\bootsize{[missing]}
\providecommand\empiricalcriticalvalue{[missing]}
\providecommand\nboot{[missing]}
\providecommand\testsize{[missing]}
\providecommand\totalsims{[missing]}
\providecommand\windowlength{[missing]}
\providecommand\empiricaltable{[missing]}

@@

\begin{document}
\maketitle

@@

The next section presents our new statistics and Section~\ref{sec:2} presents
simulations that compare our test to \poscw\ original
statistics.  Section~\ref{sec:3} demonstrates the use of our statistic
by reanalyzing \citepos{GoW:08} study of excess return
predictability and Section~\ref{sec:4} concludes. Proofs of
our results have been put in a separate Appendix along with
some minor supporting arguments \citep{Cal:14}.

@@

\begin{thm}\label{res:1}\input{mixedwindow_thm1}\end{thm}

@@

\begin{lem}\label{lem:2}\input{mixedwindow_lem2}\end{lem}

@@

Here, I conduct the same analysis, but using this paper's \mds\ test.
The benchmark model is the excess return's sample mean (as in the
original) and the alternative models are of the form
\begin{equation*}
  \mathit{excess~return}_{t} = \alpha_{0} + \alpha_{1}\
  \mathit{predictor}_{t-1} + \ep_{t},
\end{equation*}
where $\alpha_{0}$ and
$\alpha_{1}$ are estimated by \ols\ using a \windowlength-year window.
The predictors used are listed in the ``predictor'' column of
Table~\ref{tab:em1} \citep[see][for a detailed description of the
variables]{GoW:08}.  We also consider \citepos{CaT:08} proposed
correction to the models, that the forecasts be bounded below by zero
since negative forecasts are incredible, as well as two simple
combination forecasts, the mean and the median (over both the original
and the non-negative forecasts).  The data set is annual data
beginning in 1927 and ending in 2009, and the rolling window uses
\windowlength\ observations.%
\footnote{This statistical analysis was conducted in R \citep{R} and
  uses the MASS \citep[7.3-22]{VeR:02} package.} %

@@

>>>>

\documentclass[12pt,fleqn]{article}

\usepackage{amsfonts}
\usepackage{amsmath,amsthm,amssymb,graphicx,setspace,url,booktabs,tabularx,enumerate,slantsc}
\usepackage[T1]{fontenc}
\usepackage[sort,round,comma]{natbib}
\usepackage[margin=1.25in]{geometry}
\usepackage[small]{caption}
\usepackage[charter]{mathdesign}
\urlstyle{same}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\bibliographystyle{abbrvnat}
\newcommand\citepos[2][]{\citeauthor{#2}'s \citeyearpar[#1]{#2}}
\newcommand\poscw{\citeauthor{ClW:06}'s \citeyearpar{ClW:06,ClW:07}}
\newcommand\citen[1]{\citeauthor{#1}, \citeyear{#1}}
\frenchspacing
\input{tex/mcDef}
\input{tex/ap}

% These commands are generated when the monte carlo and applied
% sections are run; I'm giving them definitions now so that LaTeX will
% run.
\providecommand\bootsize{[missing]}
\providecommand\empiricalcriticalvalue{[missing]}
\providecommand\nboot{[missing]}
\providecommand\nmod{[missing]}
\providecommand\testsize{[missing]}
\providecommand\totalsims{[missing]}
\providecommand\windowlength{[missing]}
\providecommand\empiricaltable{[missing]}
\providecommand\empiricaldraws{[missing]}
\providecommand\naivecriticalvalue{[missing]}

\newtheorem{thm}{Theorem}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{claim}[thm]{Claim}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{lema}{Lemma}[section]
\newtheorem{alg}{Algorithm}
\newtheorem{asmp}{Assumption}

\theoremstyle{definition}

\newtheorem{example}{Example}
\newtheorem{defn}{Definition}
\newtheorem{rem}{Remark}

\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator{\diag}{diag}
\DeclareMathOperator{\E}{E}
\DeclareMathOperator{\var}{var}
\DeclareMathOperator{\cov}{cov}
\DeclareMathOperator*{\plim}{plim}
%\DeclareMathOperator{\vec}{vec}
\DeclareMathOperator{\vech}{vech}

\DeclareMathOperator{\pr}{Pr}

\newcommand{\iid}{\ensuremath\mathit{i.i.d.}}
\newcommand{\bernoulli}{\ensuremath\mathit{bernoulli}}

\newcommand{\Bh}{\hat{B}}
\newcommand{\btrue}[1][]{\if#1*\hat\beta_{T+1}\else\beta_0\fi}
\newcommand{\bh}{\hat{\beta}}
\newcommand{\bt}{\tilde{\beta}}
\newcommand{\ep}{\varepsilon}
\newcommand{\eph}{\hat{\varepsilon}}
\newcommand{\Fh}{\hat{F}}
\newcommand{\Fs}{\mathcal{F}}
\newcommand{\fb}{\bar{f}}
\newcommand{\fh}{\hat{f}}
\newcommand{\gb}{\bar{g}}
\newcommand{\gh}{\hat{g}}
\newcommand{\Sh}{\hat{S}}
\newcommand{\Sigmah}{\hat\Sigma}
\newcommand{\sh}{\hat\sigma}
\newcommand{\yh}{\hat{y}}

\newcommand{\X}{\ensuremath{\mathrm{X}}}
\newcommand{\R}{\ensuremath{\mathrm{R}}}
\newcommand{\p}{\ensuremath{\mathrm{P}}}

\newcommand{\osum}[1]{\sum_{#1=R+1}^T}
\newcommand{\osumb}[1]{\sum_{#1=R'+1}^T}
\newcommand{\osumc}[1]{\sum_{#1=R+1}^{R'}}
\newcommand{\oavg}[1]{\tfrac{1}{P} \osum{#1}}
\newcommand{\oclt}[1]{\tfrac{1}{\sqrt{P}} \osum{#1}}
\newcommand{\ocltb}[1]{\tfrac{1}{\sqrt{P}} \osumb{#1}}
\newcommand{\ocltc}[1]{\tfrac{1}{\sqrt{P}} \osumc{#1}}

\newcommand{\aic}{AIC}
\newcommand{\bic}{BIC}
\newcommand{\brc}{BRC}
\newcommand{\cdf}{CDF}
\newcommand{\clt}{CLT}
\newcommand{\dd}[1]{\frac{\partial}{\partial #1}}
\newcommand{\dgp}{DGP}
\newcommand{\fclt}{FCLT}
\newcommand{\fwe}{FWE}
\newcommand{\gdp}{GDP}
\newcommand{\hac}{HAC}
\newcommand{\lln}{LLN}
\newcommand{\ma}{MA}
\newcommand{\mds}{MDS}
\newcommand{\ned}{NED}
\newcommand{\ols}{OLS}
\newcommand{\oos}{OOS}
\newcommand{\sfwe}{SFWE}
\newcommand{\spa}{SPA}
\newcommand{\wfwe}{WFWE}

\renewcommand{\Re}{\ensuremath{\mathbb{R}}}

\renewcommand{\topfraction}{.85}
\renewcommand{\bottomfraction}{.7}
\renewcommand{\textfraction}{.15}
\renewcommand{\floatpagefraction}{.66}
\renewcommand{\dbltopfraction}{.66}
\renewcommand{\dblfloatpagefraction}{.66}
\setcounter{topnumber}{9}
\setcounter{bottomnumber}{9}
\setcounter{totalnumber}{20}
\setcounter{dbltopnumber}{9}

\begin{document}

@@

\maketitle

@@

The next section presents our new statistics and Section~\ref{sec:2} presents
simulations that compare our test to \poscw\ original
statistics.  Section~\ref{sec:3} demonstrates the use of our statistic
by reanalyzing \citepos{GoW:08} study of excess return
predictability. Section~\ref{sec:4} concludes.

@@

\begin{thm}\label{res:1}
  Suppose that Assumptions~\ref{a1} -- \ref{a4} hold.  Then $\sqrt{P}
  (\fb - \E f_t) \to^d N(0, \Sigma)$.
\end{thm}

@@

\begin{lem}\label{lem:2}
  Under the conditions of Thoerem~\ref{res:1}, $\Sigmah_1 \to^p
  \Sigma$. If, in addition, $y_t - x_t'\btrue$ is an MDS with respect
  to $\Fs_t$ then $\Sigmah_2 \to^p \Sigma$.
\end{lem}

@@

Here, I conduct the same analysis, but using this paper's \mds\ test.
The benchmark model is the excess return's sample mean (as in the
original) and the alternative models are of the form
\[\text{excess return}_{t} = \alpha_{0} + \alpha_{1}\ 
\text{predictor}_{t-1} + \ep_{t},\] where $\alpha_{0}$ and
$\alpha_{1}$ are estimated by \ols\ using a \windowlength-year window.
The predictors used are listed in the ``predictor'' column of
Table~\ref{tab:em1} \citep[see][for a detailed description of the
variables]{GoW:08}.  We also consider \citepos{CaT:08} proposed
correction to the models, that the forecasts be bounded below by zero
since negative forecasts are incredible, as well as two simple
combination forecasts, the mean and the median (over both the original
and the non-negative forecasts).  The data set is annual data
beginning in 1927 and ending in 2009, and the rolling window uses
\windowlength\ observations.%
\footnote{This statistical analysis was conducted in R \citep{R} and
  uses the MASS \citep[7.3-22]{VeR:02} package.} %

@@

\appendix
\section{Main theoretical results}
\label{sec:B}

\newcommand{\WesA}[1][]{\ocltb{t}
  (F_t^{#1} - \E^{#1} F_t^{#1}) B^{#1} H_t^{#1}}
\newcommand{\WesB}[1][]{\tfrac{1}{\sqrt{P}} \E^{#1}(F_t^{#1}) \osumb{t} (B_t^{#1} -
  B^{#1}) H_t^{#1}}
\newcommand{\WesC}[1][]{\ocltb{t}
  (F_t^{#1} - \E^{#1} F_t^{#1}) (B_t^{#1} - B^{#1}) H_t^{#1}}

Define the additional notation 
$F_t(\beta) = \tfrac{\partial}{\partial \beta} f_t(\beta)$,
$F_t = F_t(\btrue)$,
and
$h_t = h_t(\btrue)$.

\begin{proof}[Proof of Theorem \ref{res:1}]
  Replace $R$ with $\log(T)$ and $P$ with $T - \log(T)$ in the
  statistic; this substitution does not affect its asymptotic
  distribution.
  As in \citet{Wes:96} and \citet{WeM:98}, expand $\fh_t$ around
  $\btrue$ to get
  \begin{align*}
    \sqrt{P} \big(\fb - \fb(\btrue)\big) &= \oclt{t}
    \big(f_t - \E f_t\big) +
    \E F_t B \oclt{t} H_t \\
    & \quad + \WesA + \WesB \\ & \quad + \WesC + \oclt{t} w_t
  \end{align*}
  where (again, as in \citealp{Wes:96}) the $i$th element of $w_t$ is
  \begin{equation*}
    w_{it} = \tfrac12 (\bh_t - \btrue)'
    \Big[\tfrac{\partial^2}{\partial \beta \partial\beta'}
    f_{it}(\bt_{it}) \Big]
    (\bh_t - \btrue)
  \end{equation*}
  and each $\bt_{it}$ lies between $\bh_t$ and
  $\btrue$; $\oclt{t} w_t = o_{p}(1)$ as in Theorem~\ref{res:3}.
  Then, as before,
  \begin{gather}
    \WesA \to^{p} 0 \label{eq:11} \\
    \WesB \to^{p} 0 \label{eq:12}\\
  \intertext{and}
    \WesC \to^{p} 0 \label{eq:13}
  \end{gather}
  from Lemma~\ref{res:a4}.  The formula of the asymptotic variance can
  be derived exactly as in \citet{Wes:96} and \citet{WeM:98}.

  Note that \[f_t(\btrue)= 2 (y_{t+1} -
  x_t'\btrue)(\yh_{1,t+1} - x_t'\btrue) \quad \text{a.s.},\] as
  in \citet{ClW:07}, which is an \mds, so we do not need to use a
  \hac\ estimator of the variance under the null.  Also observe that
  \[F_t(\beta) = 2 x_t(x_t'\beta - \yh_{1,t+1}) + 2 x_t(x_t'\beta -
  y_{t+1})\] and the second term is an \mds\ under the null,
  explaining the particular form of $g_t(\beta)$.
\end{proof}

\begin{proof}[Proof of Theorem \ref{res:2}]
  Replace $R$ and $P$ as in the proof of Theorem~\ref{res:1}.
  Theorem~\ref{res:3} of this paper and Theorems~3.1 and~4.1 of
  \citet{RoW:05} complete the proof.
\end{proof}

\begin{thm}
  If the conditions of Theorem~\ref{res:1} and that $y_{t+1} -
  x_t'\btrue$ is an MDS with respect to $\Fs_t$ then $\Sigmah_2 \to^p
  \Sigma$, where $\Sigmah_2 = \Sh_{ff} + \Sh_{2,fg} + \Sh_{2,fg}' +
  \Sh_{2,gg}$, with $\Sh_{ff}$ defined earlier and
  \begin{align}
    \Sh_{fg,2} &= \oavg{t} (\fh_t - \fb) (\gh_t - \gb_2)' \\
    \Sh_{gg,2} &= \oavg{t} (\gh_{2t} - \gb_2) (\gh_{2t} - \gb_2)' \\
    \gh_{2t} &= \Bigg\{\sum_{s=\max(t, R+1)}^T \tfrac1s \Fh_s \Bh_s\Bigg\} x_{t-1} \ep_t
    \intertext{and}
    \gb_2 &= \oavg{t} \gh_{2t}.
  \end{align}
\end{thm}

\section{Supporting results}

\begin{lema}\label{res:a1}
  Suppose the conditions of Theorem~\ref{res:1} hold, and define $R'$
  to be a sequence that satisfies $R' \to \infty$ as $T \to \infty$
  and $R' = o(\sqrt{P})$. Then
  \begin{equation*}
    \ocltc{t} (\fh_t - \E f_t) \to^p 0.
  \end{equation*}
\end{lema}

\begin{proof}
  We can rewrite this summation as
  \begin{multline*}
    \ocltc{t} (\fh_t - \E f_t) = \ocltc{t} (f_t - \E f_t) + \\
    \ocltc{t} 2 (2 x_t'\btrue - y_{t+1} - \yh_{i,t+1}) x_t'(\bh_t - \btrue)
    + \ocltc{t} (x_t'\bh_t - x_t'\btrue)^2.
  \end{multline*}
  Each of these individual summations can be shown to converge to
  zero in probability. First,
  \begin{equation*}
    \E \Big\lvert \ocltc{t} (f_t - \E f_t) \Big\rvert
    \leq \ocltc{t} \E\lvert f_t - \E f_t \rvert
    = O(R'/\sqrt{P}).
  \end{equation*}
  Also,
  \begin{align*}
    \Big\lvert \ocltc{t} &2 (2 x_t'\btrue - y_{t+1} - \yh_{i,t+1}) x_t'(\bh_t - \btrue) \Big\rvert \\
    &\leq \ocltc{t} 2 \big\lvert (2 x_t'\btrue - y_{t+1} - \yh_{i,t+1}) x_t' \big\rvert
    \max_{t=R+1,\dots,R'} \lvert  \bh_t - \btrue \rvert \\
    & = O_p(R'/\sqrt{P})
  \end{align*}
  and
  \begin{equation*}
    \Big\lvert \ocltc{t} (x_t'\bh_t - x_t'\btrue)^2 \Big\rvert
    \leq \ocltc{t} \lvert x_t'x_t \rvert \max_{t=R+1,\dots,R'} (\bh_t - \btrue)'(\bh_t - \btrue)
    = O_p(R'/\sqrt{P}).
  \end{equation*}
  by Lemma~\ref{res:a2} and the \lln. Since $R'/\sqrt{P} \to 0$ by
  construction, this completes the proof.
\end{proof}

\begin{lema}\label{res:a2}
  Suppose $a \in [0,\frac12)$ and Assumptions~\ref{a1} -- \ref{a4}
  hold, and let $R'$ be a sequence such that $R' \to \infty$ as $T \to
  \infty$ and $R' = o(\sqrt{P})$. Then
  \begin{enumerate}
  \item $\sup_{t=R'+1,\dots,T} | t^a H_t | \to^p 0$.
  \item $\sup_{t=R+1,\dots,R'} | t^a H_t | = O_p(1)$.
  \item $\sup_{t = R'+1,\dots,T} | t^a(\bh_t - \btrue) | \to^{p} 0$.
  \item $\sup_{t = R+1,\dots,R'} | t^a(\bh_t - \btrue) | = O_p(1)$.
  \end{enumerate}
\end{lema}

\begin{proof}[Proof of Lemma~\ref{res:a2}]
  We will prove each part in order.
  \begin{enumerate}
  \item The process $x_{t-1} \ep_t$ is $L_2$-NED of size $-1/2$ (on
    the same mixing process as the original variables) by
    Assumption~\ref{a3}, and the moment and size conditions in that
    assumption make it an $L_2$-mixingale of size $-1/2$ as well. The
    mixingale \fclt\ implies that, for any $t \to \infty$ as $T \to \infty$,
    \begin{equation}\label{eq:2}
      t^{a - 1} \sum_{s=2}^t x_{s-1} \ep_s \to^d \lim (T^{1/2} / t^{1-a}) \cdot W(\lim t/T)
    \end{equation}
    where $W(\cdot)$ is a multivariate Gaussian process.

    If $t/T \to \gamma$ then $T^{1/2} / t^{1-a} \to 0$ and the limit
    in~\eqref{eq:2} is almost surely 0. If $t/T \to 0$, then
    \begin{equation*}
      \E\Big( t^{a - 1} \sum_{s=2}^t x_{s-1} \ep_s \Big)^2 = t^{2a - 1}\, O(1)
    \end{equation*}
    and the limit in~\eqref{eq:2} is again almost surely 0. The
    Continuous Mapping Theorem then implies that
    \begin{equation*}
      \sup_{t=R'+1,\dots,T} \Big| t^{a - 1} \sum_{s=2}^t x_{s-1} \ep_s \Big| \to^p 0.
    \end{equation*}
  \item Again, $x_{t-1} \ep_t$ is an $L_2$-mixingale of size
    $-1/2$. As a result, we can use a maximal inequality of
    \cite{Mcl:75} (also available as Corollary 16.10 in
    \citealp{Dav:94}), giving
    \begin{align*}
      \E \Big\lvert \sup_{t=R+1,\dots,R'} \Big(t^{a - 1} \sum_{s=2}^t x_{s-1} \ep_s\Big)^2 \Big\rvert
      &\leq \E \Big\lvert \sup_{t=R+1,\dots,R'} \Big(\sum_{s=2}^t s^{a-1} x_{s-1} \ep_s\Big)^2 \Big\rvert \\
      &= O(1) \sum_{s=2}^{R'} s^{2a - 2}
    \end{align*}
    which converges to a finite limit.
  \item We have
    \begin{multline*}
      \sup_{t=R'+1,\dots,T} | t^a (\hat{\beta}_t - \btrue) | \leq \\
      \sup_{t,u =R'+1,\dots,T} \Big| [ \hat{B}_u - B]
      t^{a-1} \sum_{s=2}^t x_s \ep_{s-1} \Big| + \sup_{t = R'+1,\dots,T} \Big|
      B t^{a-1} \sum_{2=1}^t x_s \ep_{s-1} \Big|
    \end{multline*}
    and both terms converge to zero in probability by Part 1 and by
    assumption.
  \item Similar to the previous argument, we have
    \begin{multline*}
      \sup_{t=R+1,\dots,R'} | t^a (\hat{\beta}_t - \btrue) | \leq \\
      \sup_{t,u =R+1,\dots,R'} \Big| [ \hat{B}_u - B]
      t^{a-1} \sum_{s=2}^t x_s \ep_{s-1} \Big| + \sup_{t = R+1,\dots,R'} \Big|
      B t^{a-1} \sum_{2=1}^t x_s \ep_{s-1} \Big|.
    \end{multline*}
    Both terms are $O_p(1)$ by Part 2 and by assumption. \qedhere
  \end{enumerate}
\end{proof}

\begin{lema}\label{res:a4}
  Under the conditions of Theorem~\ref{res:1}, Equations
  \eqref{eq:11}--\eqref{eq:13} hold.
\end{lema}

\begin{proof}[Proof of Lemma~\ref{res:a4}]
We can write
\begin{equation*}
  \Big\lvert \WesA \Big\rvert \leq
  \Big\lvert \ocltb{t} (F_t - \E F_t) B \Big\rvert
  \sup_{t = R'+1,\dots,T} | H_t |.
\end{equation*}
From Lemma~\ref{res:a2}, $\sup_{t = R'+1,\dots,T} | H_t | \to^p 0$. The \clt\ implies
that $\ocltb{t} (F_t - \E F_t) = O_p(1)$,
establishing~\eqref{eq:11}. The proofs of \eqref{eq:12}
and~\eqref{eq:13} are similar.
\end{proof}
